Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-18 doc/leanappendix.tex

%% \subsection{Evaluation}

%% [TODO: Say something to establish that the procedure run in reasonable time and produce
%% useful results; or maybe this goes in the next section?]

>>>>

\subsection{Evaluation}

\input{figure-check}

We ran the \lean{} checker on the 80 benchmark problems for which the
generated CRAT file had at most 10~million total clauses.  These are the
same benchmarks used in evaluating the optimizations (Section
\ref{app:experiment:optimize}).  Figure~\ref{fig:lean} shows the
comparative performance of the \lean{} checker versus our unverified
checker on the Y axis, with the total number of clauses on the X axis.

As would be expected, the \lean{} checker consistently runs slower
than the unverified checker.  Two of the benchmarks exceeded the time
limit of 1000 seconds with the \lean{} checker.  Of those that
completed, the ratio of the runtime for \lean{} versus the runtime for
the unverified checker had a harmonic mean of 5.9.

Importantly, however, it can be seen that both checkers show the same
overall asymptotic performance.  The ratio of the two runtimes was
less than $8.0$ for all but two very small benchmarks.  This seems like a
reasonable price to pay for a rigorous guarantee of correctness.
